---
title: "Sentiment Analysis for Amazon Review Dataset and its replications"
author: "Rong Li, Xiongjie Dai, Zixing Deng"
output: 
  beamer_presentation: default
  ioslides_presentation: 
    css: style.css
    transition: 0
    widescreen: yes
date: "2022-12-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Model 4: FastText word Embedding

- fastText: breaking words into n-grams (subwords), and generating word embeddings by taking the sum of those subwords

  - e.g. 2-grams for word *help* will be "he, el, lp"

- `fastTextR` package:

  - `ft_control`: set hyperparameter for fastText

  - `ft_train`: train the model

  - `ft_predict`: predict values based on the trained model
  
  - `ft_test`: evaluate the model

- Final results:

  - *Amazon Review* dataset: 86.48%
  
  - *Drug Review* dataset: 78.96%


## Slide with Bullets

-   Bullet 1
-   Bullet 2
-   Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
